\documentclass[hyp,12pt]{socreport}
\usepackage{color, colortbl}
\usepackage{fullpage}
\usepackage{url}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{pgf}
\usepackage{pgfplots}
\usepackage{tikz}
\usepackage{subcaption}
\usepackage[latin1]{inputenc}
\usepackage{verbatim}
\usetikzlibrary{fit}					% fitting shapes to coordinates
\usetikzlibrary{backgrounds}	% drawing the background after the foreground
\usetikzlibrary{arrows,automata,calc,patterns,snakes}

\begin{document}
\input{macros}
\pagenumbering{roman}
\title{Predicting Web 2.0 Thread Updates}
\author{Shawn Tan}
\projyear{2012}
\projnumber{H079830}
\advisor{A/P Kan Min-Yen}
\deliverables{
	\item Report: 1 Volume
}
\maketitle
\begin{abstract}
With the advent of Web 2.0, sites with forums, or similar thread-based
discussion features are increasingly common. An incremental web crawler aiming 
to maintain a database of up-to-date, extracted information from sites with such 
discussion features must strike a balance between bandwidth usage and freshness 
of data. Our objective: To estimate the arrival times of the next update to such 
threads. We demonstrate three different methods for achieving this using 
regression methods, and make recommendations as to how they can be used in a 
crawling system. We also propose a novel metric for measuring the timeliness of 
such a model that balances between the model's timeliness and bandwidth 
consumption. We show that our methods outperform the baseline, and recommend a 
way to incorporate these methods into an incremental crawler.

\begin{descriptors}
\item World Wide Web
	\begin{itemize}
	\item[] Web searching and information discovery
		\begin{itemize}
		\item[] Web search engines
			\begin{itemize}
			\item[] Web crawling
			\end{itemize}
		\end{itemize}
	\end{itemize}
	\item[] Information Retrieval
		\begin{itemize}
		\item[] Evaluation of retrieval results
			\begin{itemize}
			\item[] Retrieval effectiveness
			\end{itemize}
		\end{itemize}
\end{descriptors}
\begin{keywords}
	web crawlers, revisitation, discussion threads, evaluation metrics
\end{keywords}
\begin{implement}
	python, bash, scikit-learn\nocite{scikit-learn}
\end{implement}
\end{abstract}

\begin{acknowledgement}
I would like to express my gratitude to my parents, for supporting me throughout 
my final year of university. I would also like to thank the following friends: 
Low Wee, Yipeng, Cedric, Davin, Chris and Lan Guan.  Without them, I would not 
have had the moral support during times of stress, nor would I have been able to 
have discussions while fleshing out ideas.

Most of all, I would really like to thank Jesse and A/P Min-Yen Kan, for their 
patient guidance, support, and for the mentorship during the course of this 
project.
\end{acknowledgement}

\listoffigures 
\listoftables
\tableofcontents 

\include{introduction}
\include{related}
\include{method}
\include{metrics}
\include{evaluation}
\include{conclusion}

\bibliographystyle{socreport}
\bibliography{report}

\appendix
\chapter{Topic Modelling}\label{top_modeling}
\input{appendix}
\end{document}
